\section{Introduction}
\label{sec:intro}

The DHCD dataset~\cite{acharya2015dhcd} is now the standard benchmark for
46-class handwritten Devanagari character recognition, and reported top-1
accuracies have compressed into a narrow band above 99.7\,\%.
The leading results sit inside that band: MallaNet~\cite{malla2025} reaches 99.71\,\% with a \textbf{17.32\,M}-parameter convolutional architecture, while Mishra~\cite{mishra2021} independently reports 99.72\,\% with a similarly large model.
At this level, the benchmark no longer rewards the usual tradeoff in a clear
way: successive accuracy gains are measured in \emph{hundredths of a
percent}, yet the models claiming them still use parameter budgets far beyond
what a compact on-device recognizer can reasonably carry.
The field therefore needs to know whether the remaining gap between large and
small models is a real performance difference or just measurement noise.

Existing DHCD papers leave that question unresolved.
They typically report point accuracies, or use McNemar only against weaker
baselines, without testing the nearest competitor or giving exact $p$-values.
With a test set of $n{=}13{,}800$ samples and accuracies near 99.7\,\%,
overlapping unpaired confidence intervals are inevitable, so raw-accuracy
rankings alone have little inferential value.
The decisive question is \emph{paired}: on the same test images, do two models
actually fail on different examples?
We answer that question with the exact McNemar test---the standard paired
binary-classification significance test---for every student--teacher pair we
evaluate, alongside Wilson confidence intervals for each model's accuracy.
Because prior DHCD work omits paired testing or applies it selectively without
exact $p$-values and without testing the nearest competitor, applying the test
systematically changes the interpretation of the leaderboard.

The result is sharper than a smaller model matching a larger one.
A \textbf{1.11\,M}-parameter student reaches statistical parity with MallaNet
(McNemar $p=0.345$) using \textbf{15.6\(\times\)} fewer parameters, and the
same parity appears \emph{even without knowledge distillation}.
Across distillation targets (TTA-softened vs.\ clean no-TTA targets, and a supervised control) and teacher ensemble size (9 vs.\ 15 teachers), \emph{no lever} produces a statistically significant improvement: every model tested converges to the same \textbf{11-error intrinsic floor}, where DHCD's label noise and handwriting ambiguity dominate.
The benchmark is therefore saturated; meaningful progress now requires either
a harder evaluation set or substantially different modelling assumptions.

\medskip
\noindent\textbf{Contributions.}
\begin{itemize}
  \item[\textbf{C1.}] A compact \modelname{} student (\textbf{1.11\,M}
    parameters) achieving \textbf{99.73\,\%} on DHCD---the highest reported
    accuracy on the standard 46-class split---at \textbf{15.6\(\times\)}
    smaller footprint than prior state-of-the-art, with statistical parity
    against the nearest large baseline confirmed by McNemar ($p=0.345$), and
    tying it \emph{even without distillation}.

  \item[\textbf{C2.}] A rigorous paired evaluation protocol (exact McNemar
    tests, Wilson CIs) applied systematically across all configurations,
    showing that DHCD is \textbf{saturated} at an
    \textbf{11-error intrinsic floor} shared by every model.

  \item[\textbf{C3.}] Ablations over distillation targets (TTA-softened vs.\ clean no-TTA targets vs.\ supervised control), teacher ensemble size (9 vs.\ 15 teachers), and test-time augmentation, showing which design choices matter and which do not once statistical noise is properly controlled.

  \item[\textbf{C4.}] Efficiency, transfer, and robustness profiling:
    \modelname{} is \textbf{15.6\(\times\)} smaller and faster than
    MallaNet, transfers to CMATERdb digits (zero-shot \textbf{76.6\%};
    fine-tuned \textbf{97.8\%}), and remains far more robust to common
    corruptions (mCA \textbf{75.7\%} vs.\ \textbf{38.7\%}).

  \item[\textbf{C5.}] Fully reproducible artifacts---training code, model
    weights, distillation scripts, and evaluation harnesses---released at
    \repourl{} to facilitate future work on Devanagari recognition and
    benchmark saturation.
\end{itemize}
