\section{Related Work}
\label{sec:related}

\paragraph{Indic and Devanagari handwritten character recognition.}
The DHCD dataset~\cite{acharya2015dhcd} appeared in 2015 and quickly became
the standard 46-class benchmark for handwritten Devanagari character
recognition---a status it has held through more than a decade of architectural
refinements.
MallaNet~\cite{malla2025} is arguably the most compact entrant in that line,
coupling residual branch merging with homogeneous filter capsule (HFC) layers
to reach 99.71\,\% at 17.32\,M parameters.
Mishra et al.~\cite{mishra2021} independently report 99.72\,\% with a
comparably large architecture.
Those two numbers are, for practical purposes, indistinguishable.
A concurrent preprint pushes to 99.80\,\% on the 10-class Devanagari
\emph{digit} subset~\cite{malla2025digit}, though digit-only results are not
comparable to the 46-class task addressed here.
What the literature has not asked clearly enough is whether gains measured in
hundredths of a percent are statistically distinguishable from measurement
noise at all.

\paragraph{Knowledge distillation and compact model design.}
Hinton et al.~\cite{hinton2015distill} showed that soft probability outputs---
``dark knowledge''---from a large teacher can guide a smaller student to
match or approach teacher accuracy at substantially lower capacity.
Residual identity mappings~\cite{he2016identity} and squeeze-and-excitation
channel re-weighting~\cite{hu2018senet} have since become standard
building blocks for compact architectures that need to retain representational
power while cutting parameter counts.
These techniques are mature.
Yet to our knowledge, knowledge distillation has not previously been applied
to the 46-class DHCD benchmark, and it has rarely been stress-tested on
saturated benchmarks---settings where the performance gap between large and
small models is already buried inside sampling variation.
It seems like a natural experiment to run; it also happens to be an unusually
hard one to interpret without the right statistical tools.
Whether distillation provides a statistically significant advantage over direct
supervised training in this regime therefore remains open.

\paragraph{Statistical significance and benchmark saturation.}
Small sample counts matter more than they appear to when top models err on
fewer than 0.3\,\% of examples---raw accuracy rankings can shift from run to
run without any real difference in model quality.
McNemar's test~\cite{mcnemar1947} is the appropriate paired framework here:
by conditioning on the subset of examples where two models disagree, it stays
sensitive to genuine error-pattern differences while remaining robust to the
high base-rate of correct predictions that both classifiers share.
Wilson score intervals~\cite{wilson1927} give calibrated single-model accuracy
bounds; calibration analysis~\cite{guo2017calibration} connects model
confidence to empirical accuracy, a prerequisite for interpreting soft
distillation targets.

Applied to the Devanagari benchmark, this suite of tools exposes a gap that
is methodological, not architectural.
MallaNet~\cite{malla2025} applies McNemar against four weaker baselines but
does not test its nearest competitor (Mishra et al., 99.72\,\%), reports no
exact $p$-values, and draws no inference about saturation; earlier work reports
point estimates alone.
\modelname{} closes this gap by reporting exact McNemar $p$-values and Wilson
confidence intervals across every model comparison, including the nearest
competitor, and showing that the benchmark is saturated---that statistical
parity, rather than raw accuracy rank, is the appropriate evaluation criterion
at this operating point.
