\section{Experiments}

\subsection{Experimental Setup}
\label{sec:setup}

\paragraph{Dataset.}
We use DHCD~\cite{acharya2015dhcd}, the standard 46-class Devanagari
handwriting benchmark (36 consonants, 10 numerals): 78,200 training images
and 13,800 test images, each $32{\times}32$ greyscale.

\paragraph{Reproducing the MallaNet baseline.}
To enable sample-level McNemar comparison, we re-implemented the
MallaNet architecture of~\cite{malla2025} from the published description,
including the exact normalisation ($\text{mean}{=}0.5,\;\text{std}{=}0.5$) and
the class-index permutation implied by their data loader.  Seed~0 yields
\textbf{40 errors} on the held-out test set---\textbf{99.7101\%} accuracy---which
matches the 99.71\% figure reported in~\cite{malla2025}.

\subsection{Main Parity Result}
\label{sec:parity}

Table~\ref{tab:main} compares each \modelname{} configuration across
five independent seeds with the reproduced MallaNet baseline.

\begin{table}[t]\centering
\caption{Main result on DHCD test ($n{=}13{,}800$). Errors over 5
  seeds; McNemar vs.\ reproduced MallaNet (seed~0).}
\label{tab:main}
\begin{tabular}{lccccc}\toprule
Configuration & Params & Errors (5 seeds) & Mean$\pm$std & Acc \% & McNemar $p$ \\\midrule
\modelname, distilled (TTA)   & 1.11M & 34,39,35,39,36 & \textbf{36.6$\pm$2.1} & 99.735 & 0.345 \\
\modelname, distilled (clean) & 1.11M & 39,40,34,40,38 & 38.2$\pm$2.2 & 99.723 & 1.000 \\
\modelname, supervised        & 1.11M & 43,40,42,35,39 & 39.8$\pm$2.8 & 99.712 & 0.701 \\
MallaNet \cite{malla2025} (repro) & 17.32M & 40 & n/a & 99.710 & n/a \\\bottomrule
\end{tabular}\end{table}

The headline finding is straightforward: a 1.11\,M-parameter student sits
inside the noise floor of a 17.32\,M-parameter teacher.  In the
\textbf{distilled, TTA-targets} configuration, the student learns from 9 teacher
checkpoints (configurations A, B, C $\times$ seeds 0--2), with soft labels
produced by flip-averaged test-time augmentation over each training image (see
\S\ref{sec:kd}).  The result is \textbf{36.6$\pm$2.1} errors (99.735\%); a
two-sided McNemar $p = 0.345$ makes the compact student statistically
indistinguishable from the reproduced MallaNet at $\alpha = 0.05$.  The best
single seed reaches \textbf{34 errors} (99.754\%), with a Wilson 95\%
confidence interval of \textbf{[99.656\%, 99.824\%]}.  The compact model ties
it---at \textbf{15.6$\times$} fewer parameters.

What about the ablations?  Using clean single-pass logits from a 15-teacher pool
rather than flip-averaged targets gives $p = 1.000$ against MallaNet: same
accuracy tier, no measurable benefit from TTA soft labels.  Somewhat
surprisingly, the \emph{supervised control}---trained without any teacher signal
at all---also ties MallaNet ($p = 0.701$).  Parity is not carried by knowledge
distillation alone; the compact architecture itself is sufficient to match the
larger model.

\subsection{Comparison with Prior Work}
\label{sec:sota}

\begin{table}[t]\centering
\caption{Published results on the standard 46-class DHCD test split
  (78,200 train / 13,800 test). All accuracies from the primary sources.
  $\dagger$~McNemar test requires per-sample predictions; only available
  for the re-implemented MallaNet baseline (Table~\ref{tab:main}).}
\label{tab:sota}
\begin{tabular}{llrrl}\toprule
Model & Year & Params & Accuracy & Architecture \\\midrule
\modelname{} (ours, mean 5 seeds) & 2027 & \textbf{1.11\,M} & \textbf{99.735\,\%} & Compact SE-ResNet \\
Mishra et al.~\cite{mishra2021}   & 2021 & ${\approx}39$\,M & 99.72\,\%  & ResNet-85 \\
MallaNet~\cite{malla2025}         & 2025 & 17.32\,M         & 99.71\,\%  & Branch-merge CNN \\
Kumar et al.~\cite{kumar2023vit}  & 2023 & not reported     & 99.68\,\%  & Vision Transformer \\
Yadav et al.~\cite{yadav2024mlcnn}& 2024 & ${\approx}0.4$\,M& 99.21\,\%  & Modified LeNet-5 \\
Acharya et al.~\cite{acharya2015dhcd}& 2015 & ${\approx}0.03$\,M & 98.47\,\% & CNN baseline \\\bottomrule
\end{tabular}\end{table}

Table~\ref{tab:sota} situates \modelname{} against all published results on
this split.  The top four models are separated by only 0.07\,\%---well within
sampling noise on a 13,800-image test set---so the result is about size, not a
new accuracy ceiling.  \modelname{} is the only entry with both a verified
parameter budget under 2\,M \emph{and} accuracy above 99.5\,\%; the next
lightest model above that threshold is MallaNet at 17.32\,M
parameters~\cite{malla2025}---a \textbf{15.6$\times$} gap.

\subsection{Efficiency}
\label{sec:efficiency}

\begin{table}[t]\centering
\caption{Efficiency (single $32{\times}32$ image; CPU latency
  single-thread, mean$\pm$std over 40 runs).}
\label{tab:eff}
\begin{tabular}{lcccccc}\toprule
Model & Params & MACs & Size & Peak act. & CPU lat.\ (b1) & Tput \\\midrule
\modelname & 1.11M & 164M & 4.4MB & 2.8MB & 8.28$\pm$0.20\,ms & 151\,img/s \\
MallaNet   & 17.32M & 2434M & 69.3MB & 26.1MB & 78.8$\pm$0.89\,ms & 13.6\,img/s \\
\midrule Ratio & 15.6$\times$ & 14.8$\times$ & 15.6$\times$ & 9.5$\times$ & 9.5$\times$ & 11.1$\times$ \\\bottomrule
\end{tabular}\end{table}

\modelname{} runs at \textbf{9.5$\times$} lower CPU latency and \textbf{14.8$\times$} fewer MACs with no quantisation or pruning; accuracy parity holds.
