\subsection{DHCD to CMATERdb Digit Transfer}
\label{sec:transfer}

Does the distilled student learn digit structure, or just the visual habits of
one collection pipeline?  We probe this by running its representations on
CMATERdb~3.2.1 \cite{das2012cmaterdb}---an independently collected set of
handwritten Devanagari \emph{numerals} (digits 0--9; 10 classes).  CMATERdb
changes the scanner workflow, writers, paper stocks, and binarisation pipeline,
so the overlapping labels arrive from a visibly different source distribution.

We verified zero near-duplicate pairs between CMATERdb and DHCD at Hamming
distance $\leq$5\,bits (minimum observed: 6\,bits), ruling out contamination.
CMATERdb images are polarity-inverted before evaluation to match DHCD's
white-on-black convention.

\paragraph{Results.}
Table~\ref{tab:transfer} (upper rows) summarises the transfer outcomes.
\emph{Zero-shot}---the DHCD-trained distilled student applied directly to
CMATERdb with no CMATERdb training images---achieves \textbf{76.6$\pm$3.7\%},
versus \textbf{62.7\%} for a supervised baseline trained on DHCD digit images
only with the same 10-class head; on in-distribution DHCD the two are
statistically tied, but knowledge distillation carries a
\textbf{+14 percentage points} advantage under domain shift.
A \emph{linear probe} (frozen backbone, fresh 10-class head trained on
CMATERdb) raises accuracy to \textbf{85.4\%}, and light full
\emph{fine-tuning} (30 epochs, low learning rate) reaches \textbf{97.8\%}.

A scope note: this experiment covers only the \textbf{digit subset} (10 of
46 DHCD classes) and says nothing about transfer of the full Devanagari
character inventory.  Within that scope---after contamination and polarity
controls---the distilled student preserves substantially more useful digit
structure under dataset shift than the supervised DHCD-only baseline.

\subsection{Corruption Robustness}
\label{sec:robustness}

Out-of-distribution robustness is measured with additive Gaussian
\emph{noise}, Gaussian \emph{blur}, and \emph{contrast} reduction.  Each
is applied at five severity levels (following the ImageNet-C protocol
adapted to $32{\times}32$ greyscale images).  We report mean accuracy
across severities 1--5 (mCA) for each corruption family and overall.
Each model uses its \emph{own} training-time normalisation on the same
corrupted $[0,1]$ input images, keeping the comparison focused on robustness
rather than an asymmetric preprocessing advantage.

\begin{table}[t]\centering\caption{Transfer and corruption robustness. mCA = mean accuracy over severities 1--5.}\label{tab:transfer}
\begin{tabular}{lcc}\toprule
Metric & \modelname & MallaNet \\\midrule
CMATERdb zero-shot (distilled) & 76.6\% & n/a \\
CMATERdb fine-tuned & 97.8\% & n/a \\
Clean DHCD & 99.75\% & 99.71\% \\
mCA noise & 54.7\% & 66.9\% \\
mCA blur & 97.0\% & 37.6\% \\
mCA contrast & 75.5\% & 11.5\% \\
mCA overall & \textbf{75.7\%} & 38.7\% \\\bottomrule
\end{tabular}\end{table}

\paragraph{Results.}
\modelname{} fares approximately \textbf{2$\times$} better overall
(mCA 75.7\% vs.\ 38.7\%); the blur and contrast gaps are striking
(97.0\% vs.\ 37.6\% under \emph{blur}; 75.5\% vs.\ 11.5\% under
\emph{contrast}), likely reflecting the baseline's HFC design amplifying blur
and its fixed $(0.5, 0.5)$ normalisation being sensitive to the global
intensity shifts that contrast corruption introduces.  One clear reversal:
under \emph{additive noise}, the baseline holds up better
(mCA 66.9\% vs.\ 54.7\%)---practitioners targeting noise-heavy deployment
environments should note that the noise ranking goes the other way.
